Wide-Field Effects in Redshifted 21~cm Power Spectra

### 2015-03-18 ms.tex
Minor changes to text and bibtex file
From 61bf009:
============

In ms.tex,

(*) Change HI to H I

In eor.bib,

(*) Update bibtex reference to Taylor et al.(1999)

Foreground emission is currently the primary limitation to detection of redshifted H{\sc i} emission from the epoch of reionization. Modern radio telescopes that target this cosmological signal are typically wide-field instruments. Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide-field measurements imprint a characteristic {\it pitchfork}-shaped signature in this Fourier domain. This predicted feature is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H{\sc i} signal. With MWA data sensitivity improved by coherently averaging 12 independent snapshots aligned in local sidereal time across different observing nights, we confirm the prediction with a signal-noise ratio $>10$.

@@

The epoch of reionization (EoR) commenced following the formation of the first stars and galaxies. It is characterized by a period of non-linear growth of matter density perturbations and astrophysical evolution in the Universe's history. Detection of redshifted 21~cm radiation of H{\sc i} from this epoch is one of the most promising probes of the non-linear evolution of large scale structure characteristic of this epoch \citep{sun72,sco90,mad97,toz00,ili02}.

While sensitive instruments such as the Square Kilometre Array (SKA) with the capability of direct imaging of redshifted H{\sc i} become operational, numerous pathfinders and precursors such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, and the planned Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA) have enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14} and most of these are already operational.

The primary challenge to detection of cosmological redshifted H{\sc i} from the EoR comes from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker \citep[see, e.g.,][]{dim02,zal04,fur06,ali08,ber09,ber10,gho12}. Since the foregrounds and the signal have inherent differences in spatial isotropy and spectral smoothness \citep{mor04,mor06,bow09,liu11,par12b,dil13,pob13}, a detailed characterization of foreground emission has become essential \citep{bow09,liu09,dat10,liu11,mor12,tro12,pob13,dil14,liu14a,liu14b,thy13,thy15}.

@@

Fluctuations of redshifted H{\sc i} from the reionization epoch are extremely faint relative to the radio continuum emission from foreground objects. This poses perhaps the greatest challenge to EoR experiments and therefore merits a detailed characterization of foreground signatures in order to separate them from the desired signal.

>>>>

Foreground emission is currently the primary limitation to detection of redshifted H~{\sc i} emission from the epoch of reionization. Modern radio telescopes that target this cosmological signal are typically wide-field instruments. Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide-field measurements imprint a characteristic {\it pitchfork}-shaped signature in this Fourier domain. This predicted feature is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H~{\sc i} signal. With MWA data sensitivity improved by coherently averaging 12 independent snapshots aligned in local sidereal time across different observing nights, we confirm the prediction with a signal-noise ratio $>10$.

@@

The epoch of reionization (EoR) commenced following the formation of the first stars and galaxies. It is characterized by a period of non-linear growth of matter density perturbations and astrophysical evolution in the Universe's history. Detection of redshifted 21~cm radiation of H~{\sc i} from this epoch is one of the most promising probes of the non-linear evolution of large scale structure characteristic of this epoch \citep{sun72,sco90,mad97,toz00,ili02}.

While sensitive instruments such as the Square Kilometre Array (SKA) with the capability of direct imaging of redshifted H~{\sc i} become operational, numerous pathfinders and precursors such as the Murchison Widefield Array \citep[MWA;][]{lon09,tin13,bow13}, the Low Frequency Array \citep[LOFAR;][]{van13}, the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, and the planned Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA) have enough sensitivity for a statistical detection of the signal \citep{bow06,par12a,bea13,dil13,thy13,pob14} and most of these are already operational.

The primary challenge to detection of cosmological redshifted H~{\sc i} from the EoR comes from continuum emission from Galactic and extragalactic foreground objects, relative to which the desired signal is $\sim 10^4$ times weaker \citep[see, e.g.,][]{dim02,zal04,fur06,ali08,ber09,ber10,gho12}. Since the foregrounds and the signal have inherent differences in spatial isotropy and spectral smoothness \citep{mor04,mor06,bow09,liu11,par12b,dil13,pob13}, a detailed characterization of foreground emission has become essential \citep{bow09,liu09,dat10,liu11,mor12,tro12,pob13,dil14,liu14a,liu14b,thy13,thy15}.

@@

Fluctuations of redshifted H~{\sc i} from the reionization epoch are extremely faint relative to the radio continuum emission from foreground objects. This poses perhaps the greatest challenge to EoR experiments and therefore merits a detailed characterization of foreground signatures in order to separate them from the desired signal.
